The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete v0.3

### 2014-01-08 main/s_level_2.tex
included partial / total distinction in NCG def

% TO DO: I think we can move away from partial configurations - this requires to show that edge-gadgets always belong to the kingdom of at least one vertex-gadget

@@

A \emph{configuration} of an \textsc{ncg} is a partial function $\gamma\colon E\rightharpoonup V$ such that
\begin{itemize}
	\item
for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$, and
	\item
for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
\end{itemize}

A \emph{reconfiguration step} $\gamma\sim\delta$ connects two configurations for an \textsc{ncg} $G$ that differ in the assignment of exactly one edge.

@@

[[ NOTE: decide on notation for steps and paths in permutation relations ]]

@@

In an \textsc{ncg} $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
%
This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\int G$.

For a weight element $W$ of an edge connecting $v_i$ and $v_j$, let the $\bot$-occurrences be named as follows,
\[
	W =  \big(\named{    \dagger}\bot\tn\named{   1}\bot\tn\dotsc\tn\named{3i+1}\bot\big)
	\parr\big(\named{   \ddagger}\bot\tn\named{3i+2}\bot\tn\dotsc\tn\named{3j+1}\bot\big)
	\parr\big(\named{\downdagger}\bot\tn\named{3j+2}\bot\tn\dotsc\tn\named{3n+3}\bot\big)
\]
and the $1$-occurrences of a constraint element $C$ in $\itn{v_k}$,
\[
	C = \big(\named{    \dagger'}1\parr\named{   1'}1\parr\dotso\parr\named{3k+1'}1\big)
	\tn \big(\named{\downdagger'}1\parr\named{3k+2'}1\parr\dotso\parr\named{3n+3'}1\big)~.
\]
There is a \emph{natural linking} for the sequent $W,C$ if $e$ is appropriate for $v_k$, i.e.\ if $k=i$ or $k=j$, as follows:
\[
	\links(x) = x' \qquad \text{for }x\in\{\dagger,\downdagger\}\cup\mathbb N
\]
\[
	\links(\ddagger)=
	\begin{cases}
			\dagger' & \text{if }k=i \\
		\downdagger' & \text{if }k=j~.
	\end{cases}
\]
There is also a natural linking for the sequent $W,\named\star 1,\named{1'}1,\dotsc,\named{3n+3'}1$ consisting of the weight element $W$ and $3n+4$ edge-absorbers:
\[
	\links(x)=
	\begin{cases}
		\star & \text{if }x\in\{\dagger,\ddagger,\downdagger\} \\
		   x' & \text{otherwise }.
	\end{cases}
\]

@@

The interpretation $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
%
Let the rightmost $1$-occurrence of each vertex-gadget $\itn v$ be named $v$, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$ named $e$:
\[	
	\itn v = C\parr\dotso\parr C\parr \named v1 \qquad \itn e= W\tn\dotso\tn W\tn\named e\bot~.
\]
To define $\itn\gamma=\links$, firstly let
\[
	\links(e)=\gamma(e)~.
\]
Then successively for each edge $e$ and each weight element $W$ in $e$, if $\gamma(e)$ has a first free constraint element $C$, extend $\links$ to include the natural linking on $W,C$; otherwise, extend $\links$ by the natural linking on $W$ plus the first $3n+4$ free edge absorbers.

@@

\begin{definition}
For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links$ be the configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
\end{definition}

@@

%\begin{definition}
%The interpretation $\itn\gamma$ of a configuration $\gamma$ for a graph $G$ is the set of proof nets for $\itn G$ satisfying the following constraint: if $\gamma(e)=v$ then $\itn e$ belongs to the empire of $\itn v$
%\end{definition}

>>>>

\newcommand\alt{\underline}

[[ NOTE: we should decide on notation for steps versus paths in permutation relations ]]

@@

A (partial) \emph{configuration} of an \textsc{ncg} is a (partial) function $\gamma\colon E\to V$ such that
\begin{itemize}
	\item
for every edge $e$, $\gamma(e)\in v(e)$ or (in the partial case) $\gamma(e)$ is undefined, and
	\item
for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
\end{itemize}

A \emph{reconfiguration step} $\gamma\sim\delta$ connects two (partial) configurations for an \textsc{ncg} $G$ that differ in the assignment of exactly one edge.

@@

The \emph{(partial) \textsc{ncg}-reconfiguration problem} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.

\begin{theorem}[\cite{demaine}]
\textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
\end{theorem}

\begin{proposition}
Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
\end{proposition}

\begin{proof}
There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
%
Firstly, if $\gamma\sim\delta$ are partial configurations, they may be completed to total configurations $\gamma'\sim\delta'$ or $\gamma'=\delta'$.
%
Secondly, if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by re-assigning the values where they disagree.
%
\end{proof}

@@

In an \textsc{ncg} $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
%
This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$.

For a weight element $W$ of an edge connecting $v_i$ and $v_j$, let the $\bot$-occurrences be named as follows,
\[
	W =  \big(\named{    \dagger}\bot\tn\named{   1}\bot\tn\dotsc\tn\named{3i+1}\bot\big)
	\parr\big(\named{   \ddagger}\bot\tn\named{3i+2}\bot\tn\dotsc\tn\named{3j+1}\bot\big)
	\parr\big(\named{\downdagger}\bot\tn\named{3j+2}\bot\tn\dotsc\tn\named{3n+3}\bot\big)
\]
and the $1$-occurrences of a constraint element $C$ in $\itn{v_k}$,
\[
	C = \big(\named{\alt    \dagger}1\parr\named{\alt{   1}}1\parr\dotso\parr\named{\alt{3k+1}}1\big)
	\tn \big(\named{\alt\downdagger}1\parr\named{\alt{3k+2}}1\parr\dotso\parr\named{\alt{3n+3}}1\big)~.
\]
There is a \emph{natural linking} for the sequent $W,C$ if $e$ is appropriate for $v_k$, i.e.\ if $k=i$ or $k=j$, as follows:
\[
	\links(x) = \alt x \qquad \text{for }x\in\{\dagger,\downdagger\}\cup\mathbb N
\]
\[
	\links(\ddagger)=
	\begin{cases}
		\alt	\dagger & \text{if }k=i \\
		\alt\downdagger & \text{if }k=j~.
	\end{cases}
\]
There is also a natural linking for the sequent $W,\named\star 1,\named{\alt 1}1,\dotsc,\named{\alt {3n+3}}1$ consisting of the weight element $W$ and $3n+4$ edge-absorbers:
\[
	\links(x)=
	\begin{cases}
		\star  & \text{if }x\in\{\dagger,\ddagger,\downdagger\} \\
		\alt x & \text{otherwise }.
	\end{cases}
\]

@@

The interpretation $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
%
Let the rightmost $1$-occurrence of each vertex-gadget $\itn v$ be named $\alt v$, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$ named $\alt e$:
\[	
	\itn v = C\parr\dotso\parr C\parr \named{\alt v}1 \qquad \itn e= W\tn\dotso\tn W\tn\named{\alt e}\bot~.
\]
To define $\itn\gamma$, firstly let $\itn\gamma(e)=\alt v$ where $\gamma(e)=v$.
%
Then successively for each edge $e$ and each weight element $W$ in $e$, if $\gamma(e)$ has a first free constraint element $C$, extend $\itn\gamma$ to include the natural linking on $W,C$; otherwise, extend $\itn\gamma$ by the natural linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.

@@

\begin{definition}
For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
\end{definition}

@@
